%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
%------------------------------------


%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
%\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
% Europe
\geometry{textwidth=14cm, textheight=22cm, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage{enumitem}
\usepackage{datetime} 
\newdateformat{usvardate}{%
\THEDAY~\monthname[\THEMONTH]~\THEYEAR}
% FONTS
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}
\setmonofont[Scale=0.8]{Monaco} 
\setsansfont[Scale=0.9]{Optima Regular} 

% ---- CUSTOM COMANDS
% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}}
% ---- MARGIN YEARS
\newcommand{\virginyears}[1]{\marginpar{\scriptsize #1}}
\newcommand{\years}[1]{\noindent\virginyears{#1}}
\newcommand{\MJ}      {{\sc{Majo\-ra\-na}}}
\newcommand{\KIT}      {Karlsruher Institut f\"{u}r Technologie}
\def\minmod{{\sc Demonstrator}}
\newcommand{\cpp}{C\protect\raisebox{.25ex}{++}\ }
\newenvironment{packed_enum}{
\begin{itemize}[topsep=0pt]
  \renewcommand{\labelitemi}{$\cdot$}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}
% ---- END CUSTOM COMANDS
% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\sffamily\mdseries\scshape\large\sectionrule{0pt}{0pt}{-0.5ex}{0.5pt}} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[unicode, bookmarks,  colorlinks, breaklinks, pdftitle={Adam Cox - vita},pdfauthor={Adam Cox}]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 

% DOCUMENT
\begin{document}

%Add some length after paragraphs to improve readability
\setlength{\parskip}{1ex}

%
% Add the following command to grab *everything* from the bib database
\nocite{*}
%

\reversemarginpar
\textsf{\LARGE G.~Adam Cox}\\[1cm]
\KIT\\
Institut f\"{u}r Experimentelle Kernphysik \\
Campus Nord\\
Postfach 36 40\\
76021 Karlsruhe\\
Germany\\[.2cm]
Phone: \texttt{+49 (0)721 6082 4672}\\
Mobile: \texttt{+49 (0)1520 719 6181}\\[.2cm]
\def\myemail{adam.cox@kit.edu}
email: \href{mailto:\myemail}{\myemail}\\
%\vfill

%%\hrule
\section*{Education}
\years{2008}\textsc{PhD} in Physics, University of Washington, Seattle, Washington

\years{2003}\textsc{MSc} in Physics, University of Washington, Seattle, Washington

\years{2000}\textsc{BS} in Physics, \emph{Magna cum laude}, Arizona State Univeristy, Tempe, Arizona


%%\hrule  -- stupid lack of awards
%\section*{Awards \amper{} honors}
%\years{2015}Nobel Prize, Stockholm, Sweden

% new page to deal with funky page break
%\newpage
% Publication/Presentations
\section*{Publications \amper{} Presentations}
\subsection*{Journal articles}
% Journal articles, parse everything from bib database and order correctly
``there are definitely more than this now, including edelweiss papers"

“An Independent Measurement of the Total Active 8B Solar Neutrino Flux Using an Array of 3He Proportional Counters at the Sudbury Neutrino Observatory”, B. Aharmin, et al, Phys. Rev Lett. 101 111301, (2008)

“An array of low-background 3He proportional counters for the Sudbury Neutrino Observatory”, J. F. Amsbaugh, et al, Nucl. Instrum. Meth. A 579, 1054 (2007)

“Sudbury Neutrino Observatory Neutral Current Detectors Signal Readout System”, G. A. Cox, et al, IEEE Trans. Nucl. Sci. 51, 2227 (2004)

“Sudbury Neutrino Observatory Neutrino Current Detector Acquisition Software Overview”, M. A. Howe, et al, IEEE Trans. Nucl. Sci. 51, 878 (2004)

“Sudbury Neutrino Observatory Neutral Current Detectors Signal Readout System”, John F. Amsbaugh et al. Nucl. Instrum. Meth. A, 579, 1054-1080, 

“Measurement of the nu(e) and Total 8B Solar Neutrino Fluxes with the Sudbury Neutrino Observatory Phase I Data Set”, SNO Collaboration.  nucl-ex/0610020.

“A Search for Neutrinos from the Solar hep Reaction and the Diffuse Supernova Neutrino Background with the Sudbury Neutrino Observatory”, SNO Collaboration. ApJ 653, 1545 (2006).

“A Search for Periodicities in the 8B Solar Neutrino Flux Measured by the Sudbury Neutrino Observatory”, SNO Collaboration. Phys. Rev. D. 72 052010 (2005).

“Electron Energy Spectra, Fluxes, and Day-Night Asymmetries of 8B Solar Neutrinos from the 391-Day Salt Phase SNO Data Set”, SNO Collaboration. Phys. Rev. C. 72 055502 (2005).

“Electron Antineutrino Search at the Sudbury Neutrino Observatory”, SNO Collaboration.  Phys. Rev. D. 70 093014 (2004).

“Constraints on Nucleon Decay via Invisible Modes from the Sudbury Neutrino Observatory”, SNO Collaboration.  Phys. Rev. Lett. 92, 102004 (2004).

“Neutral Current and Day Night Measurements from the Pure D2O Phase of SNO”, SNO Collaboration. Nucl. Phys. Proc. Suppl. 118, pp. 3-14 (2003).

“Measurement of the Total Active 8B Solar Neutrino Flux at the Sudbury Neutrino Observatory with Enhanced Neutral Current Sensitivity”, SNO Collaboration. Phys. Rev. Lett. 92 181301 (2004).

“Direct Evidence for Neutrino Flavor Transformation from Neutral-Current Interactions in SNO”, SNO Collaboration. AIP Conf. Proc. 646, pp. 43-58 (2003).

“Solar Neutrino Observations at the Sudbury Neutrino Observatory”, SNO Collaboration.  Proceedings of 30th SLAC Summer Institute on Particle Physics. pp TTH01 (2002).  hep-ex/0211013.

“Measurement of CC Interactions Produced by B-8 Solar Neutrinos at SNO”, SNO Collaboration.  Prepared for International Europhysics Conference on High-Energy Physics (HEP 2001), Budapest, Hungary, 12-18 Jul 2001.

“Measurement of Day and Night Neutrino Energy Spectra at SNO and Constrains on Neutrino Mixing Parameters”, SNO Collaboration.  Phys. Rev. Lett. 89 011302 (2002).

“Direct Evidence for Neutrino Flavor Transformation from Neutral-Current Interactions in the Sudbury Neutrino Observatory”, SNO Collaboration.  Phys. Rev. Lett. 89 011301 (2002).

“First Results from the Sudbury Neutrino Observatory”, SNO Collaboration.  Prepared for the NO-VE International Workshop on Neutrino Oscillations in Venice, Italy, 24-26 Jul 2001.

“Neutrino Observations from the Sudbury Neutrino Observatory”, SNO Collaboration.  AIP Conf. Proc. 610, pp 218-230 (2002).

“Measurement of νe+d →p+p+e- Interactions Produced by 8B Solar Neutrinos at the Sudbury Neutrino Observatory”, SNO Collaboration.  Phys. Rev. Lett. 87 071301 (2001).

%\bibliographystyle{gac_cv}
%\bibliography{cv_gac}

\newpage
\subsection*{Presentations}

\years{2011}``Edelweiss at UW", CENPA Seminar, Univeristy of Washington, Seattle, Washington \emph{Invited Talk}

\years{2011} ``APS meeting"
\years{2008}``SNO's Final Solar Neutrino Flux Measurement: The NCD Phase", Institut f\"{u}r Kernphysik Seminar, Karlsruhe, Germany

\years{2005}``Event Identification in SNO's NCD Phase", APS/Japanese Physics Society - HAW05, Kanapali, Maui, Hawaii
 
\years{2003} ``Need to put in all presentations"

% new page to deal with funky page break
%\newpage
% Professional experience
\section*{Professional Experience}

\years{2010-present}{\emph{Postdoktorand}, IEKP, \KIT, Karlsruhe, Germany}
\begin{packed_enum}
	\item Member of the EDELWEISS~collaboration (WIMP Analysis)
	\item Member of the EURECA experiment (Conceptual design development)
\end{packed_enum}	

\years{2009}{\emph{Visiting Scholar}, CENPA, University of Washington, Seattle, Washington}
\begin{packed_enum}
  \item KATRIN focal-plane detector characterization and commissioning (analysis software) 
\end{packed_enum}

\years{2008-2009}{\emph{Assistant Professor}, Digipen Institute of Technology, Redmond, Washington}
\begin{packed_enum}
  \item Calculus-based 
\end{packed_enum}

\years{2008}{\emph{Postdoktorand}, IKP, \KIT, Karlsruhe, Germany}
\begin{packed_enum}
	\item Member of the KATRIN~collaboration (Bremsstrahlung production simulations for KATIN rear-wall)
\end{packed_enum}	

\years{2000-2008}{\emph{Graduate Research Assistant}, CENPA, University of Washington, Seattle, Washington\\ Advisor: John F. Wilkerson}
\begin{packed_enum}
	\item Member of the SNO~collaboration
	\item Software: 
	\item Hardware: 
	\item Analysis: 
\end{packed_enum}

\years{1999-2000}{\emph{Lab Assistant}, Ion Beam Analysis of Materials (IBeAM) Lab, Arizona St. Univerity, Tempe, Arizona}\\ {Advisor: Robert Culbertson }
\begin{packed_enum}
\item Trained to run IBeAM Tandem Accelerator ($5$~MV)
\item Debugged and wrote LabVIEW data acquisition software
\end{packed_enum}

\years{1998-1999}{\emph{Teaching Assistant}, Arizona St. Univerity, Tempe, Arizona}
\begin{packed_enum}
\item Laboratory section of introductory physics course.
\end{packed_enum}

\years{1998}{\emph{Summer Research Assistant}, NSF Research Experience for Undergraduates Program, Purdue Univeristy, West Lafayette, Indiana}\\{Advisor: Albert Chang}
\begin{packed_enum}
\item Investigation of quantum-scale electron-beam lithography on GaAs substrates utilitzing a scanning electron microscope.
\end{packed_enum}



% Outreach, not necessarily physics-based
\section*{Committes and Affiliations}
\emph{APS Member}
\begin{packed_enum}
\item Units: Division of Nuclear Physics, Division of Particles and Fields, Forum for Graduate Student Affairs, Northwest Section
\end{packed_enum}

\years{2003}{\emph{APS Forum for Graduate Student Affairs Nominating Committee}}

\emph{Society of Physics Students}, Arizona State Univeristy, Tempe, Arizona

\emph{Sigma Pi Sigma Honor Society}, Arizona State Univeristy Chapter, Tempe, Arizona

% Software and computing
\section*{Software and Computing}
\begin{packed_enum}
\item Fluent in C (DAQ software, analysis), \cpp (analysis, DAQ software), Python, ROOT software package
\item General experience with Fortran (simulation, theoretical calculations), PENELOPE, Matlab, LabVIEW, Perl, Geant4, Grid computing (Sun Grid, XGrid), Databases (SQL, CouchDB), Ja\-va\-script, HTML, XML
%\vspace{1cm}
\end{packed_enum}
\vfill{}
\hrulefill

% FILL IN THE FULL URL TO YOUR CV
%\begin{center}
%{\footnotesize \href{http://dl.dropbox.com/u/979314/cv_mgm.pdf}{http://dl.dropbox.com/u/979314/cv\_mgm.pdf} — Last updated: \usvardate\today
%}
%\end{center}


\end{document}
